### 2018-11-28 2018_nips_vigil_poster/main.tex
mino clean up
resizing table 2
last update poster vigil

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.3]{baposter}
% NIPS Workshops format

@@

\usepackage{multicol} % Required for multiple columns
\setlength{\columnsep}{1.5em} % Slightly increase the space between columns
\setlength{\columnseprule}{0mm} % No horizontal rule between columns
\usepackage{multirow}

@@

\headerbox{Abstract}{name=abstract,column=0,row=0}{
We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster. We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art. Finally, in contrast, we demonstrate that improper fine-tuning can actually reduce a model's accuracy as well.
} %headerbox

\headerbox{The MAC Model}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.60\textwidth]{../img/mac_cell.pdf}
				\label{subfig:pendulum_picture}
		}}

@@

The MAC network is a recurrent model that performs sequential reasoning,  where each step involves analyzing a part of the question followed by shifting the attention over the image. The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.  The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation. Besides, the input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map (referred to as knowledge base) from the image.
}

\headerbox{Simplified Mac Model}{name=data acquisition, column=0, below=double-pendulum}{

	Our proposed modification to the MAC network is based on two heuristic simplifications of the
	MAC cell. First, we observe that, taking the MAC cell equations as a whole, consecutive linear
	layers (with no activation in-between) can be combined as one linear layer. Next, we assume that
	dimension-preserving linear layers are invertible so as to avoid information loss. Applying this
	principle to the equations, with a careful reorganization, we can apply a single linear layer to the
	knowledge base prior to all the reasoning steps and work with this projected knowledge base as-is
	throughout the reasoning steps.

	\begin{table}[H]
		\centering
		\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
		\begin{tabular}{llll}
			\toprule
			Model        & Read Unit               & Write Unit &  Control Unit         \\
			\midrule
			MAC   &  787,969 &  524,800        &    525,313    \\
			%\midrule
			simplified MAC & 263,168  & 262,656       &    263,168 \\
			\midrule
			Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
			\bottomrule
		\end{tabular}
		\label{tab:data_properties}
	\end{table}
}

\headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{
	\begin{table}[H]
	\centering
	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\end{tabular}
	\label{tab:data_properties}
\end{table}
}

\headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}
	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_color.png}
			\label{subfig:pendulum_picture}
	}}

@@

\headerbox{References}{name=references, column=1, below=baseline}{
	\small
	\vspace{-8pt}
	\renewcommand{\refname}{}
	\bibliographystyle{abbrv}
	\bibliography{sample}
	\normalsize
	\textsl{}
	\begin{center}
		The Double Pendulum Chaotic Dataset:
		\large
		\texttt{\color{blue} https://ibm.github.io/double-pendulum-chaotic-dataset/}
	\end{center}
}

>>>>

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.35]{baposter}
% NIPS Workshops format

@@

\usepackage{multicol} % Required for multiple columns
\setlength{\columnsep}{1.5em} % Slightly increase the space between columns
\setlength{\columnseprule}{0mm} % No horizontal rule between columns
\usepackage{multirow}
\usepackage{graphicx}

@@

\headerbox{Abstract}{name=abstract,column=0,row=0}{
\begin{description}

	\item[$\bullet$] 	We introduce a variant of the MAC model (Hudson and Manning, ICLR 2018) with a simplified set of equations that achieves comparable accuracy, while training faster

	\item[$\bullet$] We evaluate both models on CLEVR and CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.

	\item[$\bullet$] We demonstrate that improper fine-tuning can reduce a model's accuracy as well.

\end{description}

} %headerbox

\headerbox{The MAC Model}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
				\label{subfig:pendulum_picture}
		}}

@@

\begin{description}
	\item[$\bullet$] The MAC network is a recurrent model that performs sequential reasoning; at each step the model analyzes the question and shifts the attention over the image
	\item[$\bullet$] The core of the model is the MAC cell, supported with an input unit that processes the question and image pair, and output unit which produces the answer.
	\item[$\bullet$] The input unit uses an LSTM to process the question in a word-by-word manner producing a sequence of contextual words and a final question representation.
	\item[$\bullet$] The input unit utilizes a pre-trained ResNet followed by two CNN layers to extract a feature map  from the image.

\end{description}

\headerbox{Simplified Mac Model (S-MAC)}{name=data acquisition, column=0, below=double-pendulum}{

	Our proposed modification to the MAC network is based on two heuristic simplifications of the
	MAC cell:

	\begin{description}

    \item[$\bullet$] 	First, we observe that, taking the MAC cell equations as a whole, consecutive linear
	layers (with no activation in-between) can be combined as one linear layer.

	\item[$\bullet$] Secondly, we assume that
	dimension-preserving linear layers are invertible so as to avoid information loss.

   \end{description}

\makebox[\textwidth]{MAC  \\[5cm] S-MAC}\\
\noindent\textbf{Control unit:} 
For both models, the question $q$ is first transformed in each step of 
the reasoning using a \emph{position-aware}
linear layer depending on $i$: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

\begin{multicols}{2}
	\noindent
	\begin{align*}
	&cq_i = W_{cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{cq}^{[d]}  \tag{c1} \\
	&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{ca}^{[1]}
	\tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
	\end{align*}
	\columnbreak
	{\color{Plum}
		\begin{align*}
		&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
		&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
		&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
		&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
		\end{align*}}
\end{multicols}

\vskip -0.6cm

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{\color{Plum}
		\begin{align*}
		&I_{ihw} = \mem_{i-1} \odot \kb_{hw} \tag{r1} \\ \\
		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
		\end{align*}}
\end{multicols}

\begin{table}[H]
	\centering
	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{llll}
		\toprule
		Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    525,313    \\
		%\midrule
		simplified MAC & 263,168  & 262,656       &    263,168 \\
		\midrule
		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
		\bottomrule
	\end{tabular}
	\label{tab:data_properties}
\end{table}

\headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{

Along with CLEVR, the authors~\cite{hudson2018compositional} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

	\begin{table}[H]
	\centering
	\scalebox{0.9}{
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models. The [Training] column indicates wall times and final accuracies on the training set. For fine-tuning, we use 30k samples of the test set, and kept the remainder for testing. The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training. The [Test] column reports the used set and the obtained test accuracies. If no fine-tuning was done, the whole indicated set was used for testing.}
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\end{tabular}}
	\label{tab:data_properties}
\end{table}
}

\headerbox{MAC limitations on CLEVR}{name=baseline, column=1, below=dataset}{

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}
	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_color.png}
			\label{subfig:pendulum_picture}
	}}

@@

\headerbox{References}{name=references, column=1, below=baseline}{
\bibliographystyle{alpha}
\bibliography{vigil_bibliograph}
}
